---
title: "01 Data Setup"
author: "Nate Breznau & Hung H.V. Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

## Setup


### Packages

Install from Github:

devtools::install_github("https://github.com/hungnguyen167/theoRy")

```{r setup}

packages <- c('theoRy',
              'tidyverse')

packages_cite <- c('theoRy',
                   'tidyverse',
                   'ggdag',
                   'daggity',
                   'QCA')

pacman::p_load(packages, character.only = T)

```

### Functions

load from subfolder
```{r funct}
source(here::here("Code", "functions", "functions.R"))
```


## Generate Model Multiverses

### 5 variables verses

#### Generate

```{r X3before}
nodes <- c("Y","Xtest","X3","X1","X2")
timing <- c(0,-2,1,-3,-3)
types <- c("otc","test","ctr","ctr", "ctr")
user_mods <- c("Y ~ Xtest + X2; Xtest ~ X1 + X2", # Model 1
                "Y ~ Xtest + X1; Xtest ~ X1 + X2", # Model 2
                "Y ~ Xtest + X1 + X2; Xtest ~ X1 + X2", # Model 3
                "Y ~ Xtest + X2; Xtest ~ X1 + X2; X3 ~ Y + Xtest", # Model 4
                "Y ~ Xtest + X2; Xtest ~ X2; X1 ~ X1" # Model 5
                )

multiverse_1 <- run_theoRy(nodes = nodes, timing = timing, types=types, include_subsets = TRUE, user_mods=user_mods)

multiverse_1 <- find_add_models(ls_theory = multiverse_1, on_ls = TRUE, 
                user_mods = c("Y ~ Xtest + X2; Xtest ~ X1 + X2; X3 ~ X3"), 
                assert_mod_num = c(7))

nodes <- c("Y","Xtest","X3","X1","X2")
timing <- c(0,-2,-1,-3,-3)
types <- c("otc","test","ctr","ctr", "ctr")

multiverse_2 <- run_theoRy(nodes = nodes, timing = timing, types=types, include_subsets = TRUE)

# Add models 6 and 7
multiverse_2 <- find_add_models(ls_theory = multiverse_2, on_ls = TRUE, 
                user_mods = c("Y ~ Xtest + X2 + X3; Xtest ~ X1 + X2; X3 ~ Xtest"), 
                assert_mod_num = c(6))


```
#### Merge and Comp

```{r mc5}
causal_matrix_1 <- as.data.frame(multiverse_2$causal_matrix) %>%
        mutate(multiverse = 2,
               model= ifelse(model == 6,
                             model, model+7))

causal_matrix_2 <- as.data.frame(multiverse_1$causal_matrix) %>%
        mutate(multiverse = 1,
               model = ifelse(model %in% c(1,2,3,4,5,7),
                              model, model+length(multiverse_1$formula_matrix$model)+7))
causal_matrix_merge <- rbind(causal_matrix_1, causal_matrix_2) %>%
    select(-prev_mod) %>%
    arrange(model)

formula_matrix_merge <- rbind(
    as.data.frame(multiverse_2$formula_matrix) %>%
        mutate(multiverse = 2,
               model= ifelse(model == 6,
                             model, model+7))
,
    as.data.frame(multiverse_1$formula_matrix) %>%
        mutate(multiverse = 1,
               model = ifelse(model %in% c(1,2,3,4,5,7),
                              model, model+length(multiverse_1$formula_matrix$model)+7))
) %>%
  arrange(model)


cmp_matrix_m1 <- add_compatible(formula_matrix_merge, ref_mod=1)

cmp_matrix_m7 <- add_compatible(formula_matrix_merge, ref_mod=7)


```



### 6 variable verse

Generating a 6 variable model multiverse takes about 3.5 hours. It will likely fail with less than 36 GB of RAM. Therefore, we save the results for the user and they can call them in the next code chunk.

```{r six_var_comp}
# nodes <- c("a","b","c","d","e","f")
# timing <- c(0,-1,-2,-3,-3, 1)
# types <- c("otc","test","ctr","ctr", "ctr","ctr")
# user_mods <- c("a ~ b + e; b ~ e + d", # Model 1
#                "a ~ b + d; b ~ e + d", # Model 2
#                "a ~ b + e + d; b ~ e + d", # Model 3
#                "a ~ b + e; b ~ e + d; f ~ a + b", # Model 4
#                "a ~ b + e; b ~ e; d ~ d", # Model 5
#                "a ~ b + e; b ~ d + c + e; c ~ e" # Model 6
#                )
# 
# 
# ls_theory <- run_theoRy(nodes = nodes, timing = timing, types=types, include_subsets = TRUE, user_mods=user_mods)

```



### Load Matricies

```{r loadm}
#ls_theory <- readRDS(here:::here("Results", "ls_theory.RDS"))
#user define Model 7
#ls_theory <- find_add_models(

#saveRDS(ls_theory, here::here("Results", "ls_theory.RDS"))

ls_theory <- readRDS(here:::here("Results", "ls_theory.RDS"))
```

### Build Set Matricies

For the analyses we want a main set matrix from which we can subset.

These measure the outcome as incompatible models.


```{r build_set_matrix}
set_matrix_m1 <- build_set_matrix(causal_matrix_merge, 
                               cmp_matrix = cmp_matrix_m1, 
                               outcome_var = "test_compatible",
                               outcome_positive = "incompatible") %>%
    mutate(outcome_m1 = outcome) %>%
    select(-outcome)

set_matrix_m7 <- build_set_matrix(causal_matrix_merge, 
                               cmp_matrix = cmp_matrix_m7, 
                               outcome_var = "test_compatible",
                               outcome_positive = "incompatible") %>%
    mutate(outcome_m7 = outcome) %>%
    select(model, outcome_m7) %>%
    subset(model != 1)

set_matrix_m7_m1 <- build_set_matrix(causal_matrix_merge, 
                               cmp_matrix = cmp_matrix_m7, 
                               outcome_var = "test_compatible",
                               outcome_positive = "incompatible") %>%
    mutate(outcome_m1 = NA,
           outcome_m7 = outcome,
           outcome_full_m1 = NA) %>%
    subset(model == 1, select = -outcome)

set_matrix_full_m1 <- build_set_matrix(causal_matrix_merge, 
                               cmp_matrix = cmp_matrix_m1, 
                               outcome_var = "full_model_compatible",
                               outcome_positive = "incompatible") %>%
    mutate(outcome_full_m1 = outcome) %>%
    select(model, outcome_full_m1)

set_matrix_full_m7 <- build_set_matrix(causal_matrix_merge, 
                               cmp_matrix = cmp_matrix_m7, 
                               outcome_var = "full_model_compatible",
                               outcome_positive = "incompatible") %>%
    mutate(outcome_full_m7 = outcome) %>%
    subset(select = c(model, outcome_full_m7))

set_matrix <- set_matrix_m1 %>%
    left_join(set_matrix_m7, by = "model") %>%
    left_join(set_matrix_full_m1, by = "model") %>%
    rbind(set_matrix_m7_m1) %>%
    left_join(set_matrix_full_m7, by = "model")

set_matrix <- set_matrix %>%
    left_join(select(cmp_matrix_m1, model, multiverse), by = "model")


rm(set_matrix_m1, set_matrix_m7, set_matrix_full_m1, set_matrix_full_m7, set_matrix_m7_m1)
```



## Subsets 


### 1. a Potential Collider

We are interested only in models with X1, X2 and X4. For this exercise we have two versions. One with reference model as Model 1, and the other as Model 7. The latter is Model 1 with the inclusion of X4 as a completely independent node. 

```{r subset}
# Reference Model 1
set_matrix_X123_only <- subset_models(set_matrix, cmp_matrix_m1, keep_only = c("X1", "X2", "X3"))

set_matrix_sub <- as.data.frame(cmp_matrix_m1) %>%
    mutate(inclX3 = ifelse(grepl("X3", unq_nodes), 1, 0)) %>%
    select(model, inclX3) 

set_matrix_X123_only <- left_join(set_matrix_X123_only, set_matrix_sub, by = "model") %>%
    subset(model != 7)

```



## Descriptive Figures

### Table 1. DAG Plots

```{r gen_plots, warning = F}
dag_plots <- plot_dag(multiverse_1, choose_plots=c(1,2,3,4,5), save_path=paste0(here::here("Results"))) 

for(plot in dag_plots){
    print(plot)
}

dag_plots <- plot_dag(multiverse_2, choose_plots=c(6,7), save_path=paste0(here::here("Results"))) 

for(plot in dag_plots){
    print(plot)
}
```

### Table 2. Example Matrix

```{r t2}
Table_2 <- subset(causal_matrix_merge, model %in% c(1,3,4,5), select = c(from, to, timing_from, timing_to, model))

write.csv(Table_2, here::here("Results", "Table_2.csv"), row.names = F)
```

### Figure X. Meta-Visualization

```{r metaplot}

# x <- subset(set_matrix_X123_only, multiverse ==1) %>%
#     rowwise() %>%
#     mutate(large = sum(c_across(X1_Xtest:X2)))

x <- as.data.frame(multiverse_1$causal_matrix) %>% group_by(model) %>%
    mutate(rows = n()) %>%
    select(model, rows)
m <- max(x$rows)
plot_dag(multiverse_1, choose_plots = multiverse_1$causal_matrix$model[multiverse_1$causal_matrix$model == x$model[x$rows == m]], save_path = paste0(here::here("Results")))

rm(x,m)

```



## Save Environment

```{r env}
save.image(here::here("Results", "01_Data_Setup.Rdata"))
```

## Colophon

```{r cphon}
sessionInfo()
```

## References


```{r cite}
packages_cite %>%
  map(citation) %>%
  print(style = "text")
```
