---
title: "01 Data Setup"
author: "Nate Breznau & Hung H.V. Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

## Setup


### Packages

Install from Github:

devtools::install_github("https://github.com/hungnguyen167/theoRy")

```{r setup}

packages <- c('theoRy',
              'tidyverse')

pacman::p_load(packages, character.only = T)

```

### Functions

```{r funct}
# function to identify and then subset models in set_matrix by their variables
subset_models <- function(set_matrix,
                          cmp_matrix,
                          keep_only = c("X1","X2","X3","X4")){
    cmp_matrix_a <- as.data.frame(cmp_matrix) %>%
    mutate(X1 = ifelse(grepl("X1", unq_nodes), 1, 0),
           X2 = ifelse(grepl("X2", unq_nodes), 1, 0),
           X3 = ifelse(grepl("X3", unq_nodes), 1, 0),
           X4 = ifelse(grepl("X4", unq_nodes), 1, 0)) %>%
    subset(select = c(model, X1, X2, X3, X4))
    X1 <- "X1"
    X2 <- "X2"
    X3 <- "X3"
    X4 <- "X4"
    if(X1 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X1 == 1)
    }
    if(X2 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X2 == 1)
    }
    if(X3 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X3 == 1)
    }
    if(X4 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X4 == 1)
    }
    if(!(X1 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X1 == 0)
        set_matrix <- set_matrix[,!grepl("X1", colnames(set_matrix))]
    }
    if(!(X2 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X2 == 0)
        set_matrix <- set_matrix[,!grepl("X2", colnames(set_matrix))]
    }
    if(!(X3 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X3 == 0)
        set_matrix <- set_matrix[,!grepl("X3", colnames(set_matrix))]
    }
    if(!(X4 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X4 == 0)
        set_matrix <- set_matrix[,!grepl("X4", colnames(set_matrix))]
    }
    
    sub_set <- cmp_matrix_a$model
    
    set_matrix <- subset(set_matrix, model %in% sub_set)
    
    return(set_matrix)
}
```

## Generate Model Multiverse

### Generate causal and formula matrix

Generating a 6 variable model multiverse takes about 3.5 hours. It will likely fail with less than 36 GB of RAM. Therefore, we save the results for the user and they can call them in the next code chunk.

```{r six_var_comp}
nodes <- c("a","b","c","d","e","f")
timing <- c(0,-1,-2,-3,-3, 1)
types <- c("otc","test","ctr","ctr", "ctr","ctr")
user_mods <- c("a ~ b + e; b ~ e + d", # Model 1
               "a ~ b + d; b ~ e + d", # Model 2
               "a ~ b + e + d; b ~ e + d", # Model 3
               "a ~ b + e; b ~ e + d; f ~ a + b", # Model 4
               "a ~ b + e; b ~ e; d ~ d", # Model 5
               "a ~ b + e; b ~ d + c + e; c ~ e" # Model 6
               )


ls_theory <- theoRy(nodes = nodes, timing = timing, types=types, include_subsets = TRUE, user_mods=user_mods)

```

### Load Matricies

```{r loadm}
#saveRDS(ls_theory, here::here("Results", "ls_theory.RDS"))

ls_theory <- readRDS(here:::here("Results", "ls_theory.RDS"))
```

### Compatibility Matrix

We build two. One  with reference Model 1, and then a later one with ref Model 7 which is Model 1 plus a completely independent X4 

```{r cmp}
#cmp_matrix <- add_compatible(ls_theory$formula_matrix, ref_mod = 1)

#user define Model 7
#ls_theory <- find_add_models(ls_theory = ls_theory, on_ls = TRUE, user_mods = c("a ~ b + e; b ~ e + d; f ~ f"), assert_mod_num = c(7))

#cmp_matrix_7 <- add_compatible(ls_theory$formula_matrix, ref_mod = 7)

#saveRDS(cmp_matrix, here::here("Results", "cmp_matrix.RDS"))

#saveRDS(cmp_matrix_7, here::here("Results", "cmp_matrix_7.RDS"))

cmp_matrix <- readRDS(here::here("Results", "cmp_matrix.RDS"))

cmp_matrix_7 <- readRDS(here::here("Results", "cmp_matrix_7.RDS"))

```


### Build Set Matricies

For the analyses we want a main set matrix from which we can subset.

These measure the outcome as incompatible models.


```{r build_set_matrix}
set_matrix <- build_set_matrix(ls_theory$causal_matrix, 
                               cmp_matrix = cmp_matrix, 
                               outcome_var = "test_compatible",
                               outcome_positive = "incompatible")

set_matrix_full <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix, outcome_var= "full_model_compatible", outcome_positive = "incompatible")

set_matrix_7 <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix_7, outcome_var= "test_compatible", outcome_positive = "incompatible")

set_matrix_full_7 <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix_7, outcome_var= "full_model_compatible", outcome_positive = "incompatible")
```




## Descriptive Figures

### Table 1. DAG Plots

```{r gen_plots, warning = F}
dag_plots <- plot_dag(ls_theory, choose_plots=c(1,2,3,4,5,6), save_path=paste0(here::here("Results"))) 

for(plot in dag_plots){
    print(plot)
}
```

### Table 2. Example Matrix

```{r t2}
Table_2 <- subset(ls_theory$causal_matrix, model %in% c(1,3,4,5), select = c(from, to, timing_from, timing_to, model))

write.csv(Table_2, here::here("Results", "Table_2.csv"), row.names = F)
```

## Colophon

```{r cphon}
sessionInfo()
```

## References


```{r cite}
packages %>%
  map(citation) %>%
  print(style = "text")
```
