---
title: "01 Data Setup"
author: "Nate Breznau & Hung H.V. Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

## Setup


### Packages

Install from Github:

devtools::install_github("https://github.com/hungnguyen167/theoRy")

```{r setup}

library('theoRy')

```

### Functions

```{r funct}
# function to identify and then subset models in set_matrix by their variables
subset_models <- function(set_matrix,
                          cmp_matrix,
                          keep_only = c("X1","X2","X3","X4")){
    cmp_matrix_a <- as.data.frame(cmp_matrix) %>%
    mutate(X1 = ifelse(grepl("X1", unq_nodes), 1, 0),
           X2 = ifelse(grepl("X2", unq_nodes), 1, 0),
           X3 = ifelse(grepl("X3", unq_nodes), 1, 0),
           X4 = ifelse(grepl("X4", unq_nodes), 1, 0)) %>%
    subset(select = c(model, X1, X2, X3, X4))
    X1 <- "X1"
    X2 <- "X2"
    X3 <- "X3"
    X4 <- "X4"
    if(X1 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X1 == 1)
    }
    if(X2 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X2 == 1)
    }
    if(X3 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X3 == 1)
    }
    if(X4 %in% keep_only){
        cmp_matrix_a <- subset(cmp_matrix_a, X4 == 1)
    }
    if(!(X1 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X1 == 0)
        cmp_matrix_a <- cmp_matrix_a[,!grepl("X1", colnames(cmp_matrix_a))]
    }
    if(!(X2 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X2 == 0)
        cmp_matrix_a <- cmp_matrix_a[,!grepl("X2", colnames(cmp_matrix_a))]
    }
    if(!(X3 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X3 == 0)
        cmp_matrix_a <- cmp_matrix_a[,!grepl("X3", colnames(cmp_matrix_a))]
    }
    if(!(X4 %in% keep_only)){
        cmp_matrix_a <- subset(cmp_matrix_a, X4 == 0)
        cmp_matrix_a <- cmp_matrix_a[,!grepl("X4", colnames(cmp_matrix_a))]
    }
    
    sub_set <- cmp_matrix_a$model
    
    set_matrix <- subset(set_matrix, model %in% sub_set)
    
    return(set_matrix)
}
```

## Generate Model Multiverse

### Generate causal and formula matrix

Generating a 6 variable model multiverse takes about 3.5 hours. It will likely fail with less than 36 GB of RAM. Therefore, we save the results for the user and they can call them in the next code chunk.

```{r six_var_comp}
nodes <- c("a","b","c","d","e","f")
timing <- c(0,-1,-2,-3,-3, 1)
types <- c("otc","test","ctr","ctr", "ctr","ctr")
user_mods <- c("a ~ b + e; b ~ e + d", # Model 1
               "a ~ b + d; b ~ e + d", # Model 2
               "a ~ b + e + d; b ~ e + d", # Model 3
               "a ~ b + e; b ~ e + d; f ~ a + b", # Model 4
               "a ~ b + e; b ~ e; d ~ d", # Model 5
               "a ~ b + e; b ~ d + c + e; c ~ e" # Model 6
               )


ls_theory <- theoRy(nodes = nodes, timing = timing, types=types, include_subsets = TRUE, user_mods=user_mods)

```

### Load Matricies

```{r loadm}
#saveRDS(ls_theory, here::here("Results", "ls_theory.RDS"))

ls_theory <- readRDS(here:::here("Results", "ls_theory.RDS"))
```

### Compatibility Matrix

We build two. One  with reference Model 1, and then a later one with ref Model 7 which is Model 1 plus a completely independent X4 

```{r cmp}
#cmp_matrix <- add_compatible(ls_theory$formula_matrix, ref_mod = 1)

#user define Model 7
#ls_theory <- find_add_models(ls_theory = ls_theory, on_ls = TRUE, user_mods = c("a ~ b + e; b ~ e + d; f ~ f"), assert_mod_num = c(7))

#cmp_matrix_7 <- add_compatible(ls_theory$formula_matrix, ref_mod = 7)

#saveRDS(cmp_matrix, here::here("Results", "cmp_matrix.RDS"))

#saveRDS(cmp_matrix_7, here::here("Results", "cmp_matrix_7.RDS"))

cmp_matrix <- readRDS(here::here("Results", "cmp_matrix.RDS"))

cmp_matrix_7 <- readRDS(here::here("Results", "cmp_matrix_7.RDS"))

```


### Build Set Matricies

For the analyses we want a main set matrix from which we can subset.

These measure the outcome as incompatible models.


```{r build_set_matrix}
set_matrix <- build_set_matrix(ls_theory$causal_matrix, 
                               cmp_matrix = cmp_matrix, 
                               outcome_var = "test_compatible",
                               outcome_positive = "incompatible")

set_matrix_full <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix, outcome_var= "full_model_compatible", outcome_positive = "incompatible")

set_matrix_7 <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix_7, outcome_var= "test_compatible", outcome_positive = "incompatible")

set_matrix_full_7 <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix_7, outcome_var= "full_model_compatible", outcome_positive = "incompatible")
```




## Descriptive Figures

### Table 1. DAG Plots

```{r gen_plots, warning = F}
dag_plots <- plot_dag(ls_theory, choose_plots=c(1,2,3,4,5,6), save_path=paste0(here::here("Results"))) 

for(plot in dag_plots){
    print(plot)
}
```

### Table 2. Example Matrix

```{r t2}
Table_2 <- subset(ls_theory$causal_matrix, model %in% c(1,3,4,5), select = c(from, to, timing_from, timing_to, model))

write.csv(Table_2, here::here("Results", "Table_2.csv"), row.names = F)
```




### Single Components

This can help us understand the role of single components. However, for most causal models a single component is rarely alone so important. For example a node often requires specific edges before it becomes important (e.g., becomes a confounder or collider)

```{r qca}
#set_truth <- truthTable(set_matrix_c, "outcome")

set_pof <- pof(setms = select(set_matrix, -c(model,outcome, Xtest_Y)), outcome = "outcome", data = set_matrix)

# try option relation = "sufficiency"

#inclN = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
#covN = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
#RoN = relevence of necessity = is a necessary condition trivial

set_pof
```


### Multiple Component Analyses

#### Minimize

Looking at only positive outcomes (outcome = 1/MAS = {X1}), this procedure tries to find minimal sets of variables that are present in all positive cases, regardless of if these sets are present in outcome = 0 cases.

```{r minimize}

min_results <- minimize(set_matrix_c, details = TRUE, outcome = "outcome")

```


#### Subsets

*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevence of necessity = how trivial is a necessary condition trivial = 0 or relevant = 1
```{r qca}
s_subset <- superSubset(set_matrix_c, outcome = "outcome")

s_subset
```
### Comparing the same # of variables

We have included all subsets. So these models have different variables. We might want to know about all causal models with a fixed set of variables. 


#### Subset list

```{r subs}
models_X1X2X4 <- subset(subset_models, X1 == 1 & X2 == 1 & X3 == 0 & X4 == 1, select = model)$model

set_matrix_X1X2X4 <- subset(set_matrix, model %in% models_X1X2X4)
# flip to not_compatible

set_matrix_full_comp_X1X2X4 <- subset(set_matrix_full_comp, model %in% models_X1X2X4)

set_matrix_X1X2X4 <- set_matrix_X1X2X4 %>%
    mutate(outcome = (outcome-1)*-1)

set_matrix_full_comp_X1X2X4 <- set_matrix_full_comp_X1X2X4 %>%
    mutate(outcome = (outcome-1)*-1)

```

#### Subset X1X2X4 Test Compatible

So far this keeps M1 as the comparison model. Keep that in mind. 

We flipped the outcome because we want to know which are not test_compatible


*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevence of necessity = is a necessary condition trivial

Here we find that of all models with X1, X2 and X4, `r round(mean(set_matrix_X1X2X4$outcome)*100,1)`% are not test compatible with M1. If all models were equally plausible, a fair majority would not be test compatible with M1. 

```{r subX1X2X4}
REDO THIS without the X3 variables

s_subset_X1X2X4 <- superSubset(dplyr::select(set_matrix_X1X2X4, -c(model, Xtest_Y)), outcome = "outcome")

s_subset_X1X2X4
```


#### Subset X1X2X4 full model compatible

Again the inverse. So not full model compatible. 


```{r subfullx1x2x4}
s_subset_full_X1X2X4 <- superSubset(dplyr::select(set_matrix_full_comp_X1X2X4, -c(model, Xtest_Y)), outcome = "outcome")

s_subset_full_X1X2X4
```

None are compatible. Thats because our model does not have X4. To simulate this we need to compare a version of M1 that has a solo X4 (no paths to it) and compare that at full_model_compatible.

We generate a new cmp_matrix for this. First we find the model number for the model with a solo X4 and give it number 7. 

#### Set w/ X4 alone

```{r next}


# identify models by their variables
subset_models_7 <- as.data.frame(cmp_matrix_7) %>%
    mutate(X1 = ifelse(grepl("X1", unq_nodes), 1, 0),
           X2 = ifelse(grepl("X2", unq_nodes), 1, 0),
           X3 = ifelse(grepl("X3", unq_nodes), 1, 0),
           X4 = ifelse(grepl("X4", unq_nodes), 1, 0)) %>%
    subset(select = c(model, X1, X2, X3, X4))

models_X1X2X4_7 <- subset(subset_models_7, X1 == 1 & X2 == 1 & X3 == 0 & X4 == 1, select = model)$model

set_matrix_X1X2X4_full_7 <- subset(set_matrix_full_7, model %in% models_X1X2X4_7)

set_matrix_X1X2X4_7 <- subset(set_matrix_7, model %in% models_X1X2X4_7)

# remove variables with X3 as they are all 0
set_matrix_X1X2X4_7 <- set_matrix_X1X2X4_7[,!grepl("X3", colnames(set_matrix_X1X2X4_7))]

set_matrix_X1X2X4_full_7 <- set_matrix_X1X2X4_full_7[,!grepl("X3", colnames(set_matrix_X1X2X4_full_7))]



# make incompatible as the full model

set_matrix_X1X2X4_7 <- set_matrix_X1X2X4_7 %>%
    mutate(outcome = (outcome-1)*-1)

set_matrix_X1X2X4_full_7 <- set_matrix_X1X2X4_full_7 %>%
    mutate(outcome = (outcome-1)*-1)


```

#### Analyze New Set

```{r newwX4}

s_subset_X1X2X4_7 <- superSubset(dplyr::select(set_matrix_X1X2X4_7, -c(model, Xtest_Y)), outcome = "outcome", ron.cut = 0.001)

s_subset_X1X2X4_7
```



```{r obs}
s_subset_X1X2X4_full_7 <- superSubset(dplyr::select(set_matrix_X1X2X4_full_7, -c(model, Xtest_Y)), outcome = "outcome", ron.cut = 0.001)

s_subset_X1X2X4_full_7

analyze single models!
```


