---
title: "02 Working Paper"
author: "Nate Breznau & Hung H.V. Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

## Setup


```{r setup}

library('theoRy')
library('QCA')

```

## 1. A Potential Collider

### Subset

We are interested only in models with X1, X2 and X4.

```{r subset}
set_matrix_X124 <- subset_models(set_matrix = set_matrix,
                                 cmp_matrix = cmp_matrix,
                                 keep_only = c(X1,X2,X4))

set_matrix_full_X124 <- subset_models(set_matrix_full = set_matrix,
                                 cmp_matrix = cmp_matrix,
                                 keep_only = c(X1,X2,X4))
```

*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevence of necessity = is a necessary condition trivial


### Single Components

```{r qca}
#set_truth <- truthTable(set_matrix_c, "outcome")

set_matrix_X124_pof <- pof(setms = select(set_matrix, -c(model,outcome, Xtest_Y)), outcome = "outcome", data = set_matrix)

set_pof
```


### Multiple Component Analyses

#### Minimize

Looking at only positive outcomes (outcome = 1/MAS = {X1}), this procedure tries to find minimal sets of variables that are present in all positive cases, regardless of if these sets are present in outcome = 0 cases.

```{r minimize}

min_results <- minimize(set_matrix_c, details = TRUE, outcome = "outcome")

```


#### Subsets

*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevence of necessity = how trivial is a necessary condition trivial = 0 or relevant = 1
```{r qca}
s_subset <- superSubset(set_matrix_c, outcome = "outcome")

s_subset
```
### Comparing the same # of variables

We have included all subsets. So these models have different variables. We might want to know about all causal models with a fixed set of variables. 

#### Identify vars

```{r var_find}
# identify models by their variables
subset_models <- as.data.frame(cmp_matrix) %>%
    mutate(X1 = ifelse(grepl("X1", unq_nodes), 1, 0),
           X2 = ifelse(grepl("X2", unq_nodes), 1, 0),
           X3 = ifelse(grepl("X3", unq_nodes), 1, 0),
           X4 = ifelse(grepl("X4", unq_nodes), 1, 0)) %>%
    subset(select = c(model, X1, X2, X3, X4))


```

#### Subset list

```{r subs}
models_X1X2X4 <- subset(subset_models, X1 == 1 & X2 == 1 & X3 == 0 & X4 == 1, select = model)$model

set_matrix_X1X2X4 <- subset(set_matrix, model %in% models_X1X2X4)
# flip to not_compatible

set_matrix_full_comp_X1X2X4 <- subset(set_matrix_full_comp, model %in% models_X1X2X4)

set_matrix_X1X2X4 <- set_matrix_X1X2X4 %>%
    mutate(outcome = (outcome-1)*-1)

set_matrix_full_comp_X1X2X4 <- set_matrix_full_comp_X1X2X4 %>%
    mutate(outcome = (outcome-1)*-1)

```

#### Subset X1X2X4 Test Compatible

So far this keeps M1 as the comparison model. Keep that in mind. 

We flipped the outcome because we want to know which are not test_compatible


*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevence of necessity = is a necessary condition trivial

Here we find that of all models with X1, X2 and X4, `r round(mean(set_matrix_X1X2X4$outcome)*100,1)`% are not test compatible with M1. If all models were equally plausible, a fair majority would not be test compatible with M1. 

```{r subX1X2X4}
REDO THIS without the X3 variables

s_subset_X1X2X4 <- superSubset(dplyr::select(set_matrix_X1X2X4, -c(model, Xtest_Y)), outcome = "outcome")

s_subset_X1X2X4
```


#### Subset X1X2X4 full model compatible

Again the inverse. So not full model compatible. 


```{r subfullx1x2x4}
s_subset_full_X1X2X4 <- superSubset(dplyr::select(set_matrix_full_comp_X1X2X4, -c(model, Xtest_Y)), outcome = "outcome")

s_subset_full_X1X2X4
```

None are compatible. Thats because our model does not have X4. To simulate this we need to compare a version of M1 that has a solo X4 (no paths to it) and compare that at full_model_compatible.

We generate a new cmp_matrix for this. First we find the model number for the model with a solo X4 and give it number 7. 

#### Set w/ X4 alone

```{r next}
ls_theory <- find_add_models(ls_theory = ls_theory, on_ls = TRUE, user_mods = c("a ~ b + e; b ~ e + d; f ~ f"), assert_mod_num = c(7))

cmp_matrix_7 <- add_compatible(ls_theory$formula_matrix, ref_mod = 7)

set_matrix_7 <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix_7, outcome_var= "test_compatible")

set_matrix_full_7 <-  build_set_matrix(ls_theory$causal_matrix, cmp_matrix = cmp_matrix_7, outcome_var= "full_model_compatible")

# identify models by their variables
subset_models_7 <- as.data.frame(cmp_matrix_7) %>%
    mutate(X1 = ifelse(grepl("X1", unq_nodes), 1, 0),
           X2 = ifelse(grepl("X2", unq_nodes), 1, 0),
           X3 = ifelse(grepl("X3", unq_nodes), 1, 0),
           X4 = ifelse(grepl("X4", unq_nodes), 1, 0)) %>%
    subset(select = c(model, X1, X2, X3, X4))

models_X1X2X4_7 <- subset(subset_models_7, X1 == 1 & X2 == 1 & X3 == 0 & X4 == 1, select = model)$model

set_matrix_X1X2X4_full_7 <- subset(set_matrix_full_7, model %in% models_X1X2X4_7)

set_matrix_X1X2X4_7 <- subset(set_matrix_7, model %in% models_X1X2X4_7)

# remove variables with X3 as they are all 0
set_matrix_X1X2X4_7 <- set_matrix_X1X2X4_7[,!grepl("X3", colnames(set_matrix_X1X2X4_7))]

set_matrix_X1X2X4_full_7 <- set_matrix_X1X2X4_full_7[,!grepl("X3", colnames(set_matrix_X1X2X4_full_7))]



# make incompatible as the full model

set_matrix_X1X2X4_7 <- set_matrix_X1X2X4_7 %>%
    mutate(outcome = (outcome-1)*-1)

set_matrix_X1X2X4_full_7 <- set_matrix_X1X2X4_full_7 %>%
    mutate(outcome = (outcome-1)*-1)


```

#### Analyze New Set

```{r newwX4}

s_subset_X1X2X4_7 <- superSubset(dplyr::select(set_matrix_X1X2X4_7, -c(model, Xtest_Y)), outcome = "outcome", ron.cut = 0.001)

s_subset_X1X2X4_7
```



```{r obs}
s_subset_X1X2X4_full_7 <- superSubset(dplyr::select(set_matrix_X1X2X4_full_7, -c(model, Xtest_Y)), outcome = "outcome", ron.cut = 0.001)

s_subset_X1X2X4_full_7

analyze single models!
```


