---
title: "02 Working Paper"
author: "Nate Breznau & Hung H.V. Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

## Setup


```{r setup}

packages <- c('theoRy',
              'QCA',
              'tidyverse') 

pacman::p_load(packages, character.only = T)

```

## Load 01_Data_Setup

```{r data}
load(here::here("Results", "01_Data_Setup.Rdata"))
```

## 1. A Potential Collider


### Table 3. Model Comparison Stats


```{r tbl3}
tbl3 <- matrix(nrow = 14, ncol = 4)

tbl3[,1] <- c("Model 1 Comparisons", "Reference Model", "Multiverse Criteria", "All Models Compared", "N Comparison Models", "Test Compatible =", "Full Model Compatible =", "Model 7 Comparisons", "Reference Model", "Multiverse Criteria", "All Models compared", "N Comparison Models", "Test Compatible", "Full Model Compatible")

set_matrixm <- subset(set_matrix, multiverse == 1)
set_matrixm123 <- subset(set_matrix_X123_only, multiverse == 1)
# this can be done with set_matrix

tbl3[,2] <- c("", paste0(formula_matrix_merge$formula[formula_matrix_merge$model == 1],"(Model 1)"), "Models with X1 and X2, and models with X1, X2 and X3", "", nrow(set_matrixm), 
              paste0(round(100-(100*(nrow(set_matrixm[set_matrixm$outcome_m1 == 1,])/nrow(set_matrixm))),1),"%"),
              paste0(round(100-(100*(nrow(set_matrixm[set_matrixm$outcome_full_m1 == 1,])/nrow(set_matrixm))),1),"%"),
              "", paste0(formula_matrix_merge$formula[formula_matrix_merge$model == 7],"(Model 7)"), "Models with X1, X2 and X3", "", nrow(set_matrixm),
              paste0(round(100-(100*(nrow(set_matrixm[set_matrixm$outcome_m7 == 1,])/nrow(set_matrixm))),1),"%"),
              paste0(round(100-(100*(nrow(set_matrixm[set_matrixm$outcome_full_m7 == 1,])/nrow(set_matrixm))),1),"%"))

tbl3[,3] <- c("", "", "", "Only Models w X4 Compared", "N Comparison Models", "Test Compatible =", "Full Model Compatible =", "", "", "", "Only Models w X4 Compared", "N Comparison Models", "Test Compatible", "Full Model Compatible")

tbl3[,4] <- c("", "", "", "", nrow(set_matrixm123), 
              paste0(round(100-(100*(nrow(set_matrixm123[set_matrixm123$outcome_m1 == 1,])/nrow(set_matrixm123))),1),"%"),
              paste0(round(100-(100*(nrow(set_matrixm123[set_matrixm123$outcome_full_m1 == 1,])/nrow(set_matrixm123))),1),"%"),
              "", "", "", "",
              nrow(set_matrixm123), 
              paste0(round(100-(100*(nrow(set_matrixm123[set_matrixm123$outcome_m7 == 1,])/nrow(set_matrixm123))),1),"%"),
              paste0(round(100-(100*(nrow(set_matrixm123[set_matrixm123$outcome_full_m7 == 1,])/nrow(set_matrixm123))),1),"%")
              )

write.csv(tbl3, here::here("Results", "Table_3.csv"), row.names = F)
```

### Incorrect Adjustment

Models that are incorrectly adjusted out of the multiverse for Model 1.

```{r adstats}

```

### Model 1 base multiverse

We subset models to have the same components of Model 1, with X4 being the only uncertain node and vary all paths with it. 


```{r subverseX4}
# find models with Model 1 paths constant


```

### Single Components

When all models include the same variables, it is not necessary to use their nodes as predictors. In the first two examples, X1 and X2 are in all models, and in the second two X1, X2 and X4. Therefore these should be removed as single components as their presence implies no arrows going to them and leads to confounding of the effect we are searching for. 


*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevance of necessity = is a necessary condition trivial

```{r qca}

# make multiverse specific set_matricies
set_matrixm <- subset(set_matrix, multiverse == 1)

set_matrixm123 <- subset(set_matrix_X123_only, multiverse == 1)

pof_set_matrix_mverse1 <- pof(setms = subset(set_matrix_X123_only, model != 1 & multiverse == 1, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_m1", data = subset(set_matrix_X123_only, model != 1 & multiverse == 1))

pof_set_matrix_mverse2 <- pof(setms = subset(set_matrix_X123_only, model != 1 & multiverse == 2, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_m1", data = subset(set_matrix_X123_only, model != 1 & multiverse == 2))

pof_full_set_matrix_mverse1 <- pof(setms = subset(set_matrix_X123_only, model != 1 & multiverse == 1, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_full_m1", data = subset(set_matrix_X123_only, model != 1 & multiverse == 1))

pof_full_set_matrix_mverse2 <- pof(setms = subset(set_matrix_X123_only, model != 1 & multiverse == 1, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_full_m1", data = subset(set_matrix_X123_only, model != 1 & multiverse == 1))

#Model 7
pof_m7_set_matrix_mverse1 <- pof(setms = subset(set_matrix_X123_only, model != 7 & multiverse == 1, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_m7", data = subset(set_matrix_X123_only, model != 7 & multiverse == 1))

pof_m7_set_matrix_mverse2 <- pof(setms = subset(set_matrix_X123_only, model != 7 & multiverse == 2, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_m7", data = subset(set_matrix_X123_only, model != 7 & multiverse == 2))

pof_m7_full_set_matrix_mverse1 <- pof(setms = subset(set_matrix_X123_only, model != 7 & multiverse == 1, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_full_m7", data = subset(set_matrix_X123_only, model != 7 & multiverse == 1))

pof_m7_full_set_matrix_mverse2 <- pof(setms = subset(set_matrix_X123_only, model != 7 & multiverse == 1, -c(model, outcome_m1:outcome_full_m7, Xtest_Y, X1, X2, X3, multiverse)), outcome = "outcome_full_m7", data = subset(set_matrix_X123_only, model != 7 & multiverse == 1))

# testing the high scoring combinations
#FigX lower-left
pof_set_matrix_full_m7_set1  <- pof(setms = X1_Y*X1_Xtest, outcome = "outcome_m7", data = subset(set_matrixm123, model != 7))
pof_set_matrix_full_m7_set1

#FigX lower-right
pof_set_matrix_full_m7_set2  <- pof(setms = Xtest_X3*Y_X3, outcome = "outcome_m7", data = set_matrixm123)
pof_set_matrix_full_m7_set2

#FigX upper-right
set_matrix_full_7_X124_X4only_pof_set <- pof(Xtest_X3*Y_X3 <- outcome_full_m7, data = set_matrixm123)
set_matrix_full_7_X124_X4only_pof_set

#FigX upper-left
set_matrix_full_7_X124_X4only_pof_set1 <- pof(X1_X3*X2_X3, outcome = "outcome_full_m7", data = set_matrixm123)
set_matrix_full_7_X124_X4only_pof_set1

pof_set_matrix_mverse1
pof_full_set_matrix_mverse1
pof_m7_set_matrix_mverse1
pof_m7_full_set_matrix_mverse1

```


### Multiple Components

#### Minimize

Looking at only positive outcomes (outcome = 1/MAS = {X1}), this procedure tries to find minimal sets of variables that are present in all positive cases, regardless of if these sets are present in outcome = 0 cases.

```{r minimize}

#tt_set_matrix_X124 <- truthTable(select(set_matrix_X124, -c(model, outcome_full, Xtest_Y, X1, X2, inclX4, X4), outcome = "outcome"))

min_results_X124 <- minimize(dplyr::select(set_matrix_X123_only, -c(model, outcome_full, Xtest_Y, X1, X2, X4)), details = TRUE, outcome = "outcome")

min_results_full_X124 <- minimize(dplyr::select(set_matrix_X124, -c(model, outcome, Xtest_Y, X1, X2, X4)), details = TRUE, outcome = "outcome_full")

min_results_7_X124 <- minimize(dplyr::select(set_matrix_7_X124, -c(model, outcome_full, Xtest_Y, X1, X2, X4)), details = TRUE, outcome = "outcome")

min_results_7_X124_X4only <- minimize(dplyr::select(set_matrix_7_X124_X4only, -c(model, outcome_full, Xtest_Y, X1, X2, X4)), details = TRUE, outcome = "outcome")

min_results_full_7_X124_X4only <- minimize(dplyr::select(set_matrix_7_X124_X4only, -c(model, outcome, Xtest_Y, X1, X2, X4)), details = TRUE, outcome = "outcome_full")


min_results_7_X124_X4only
min_results_full_7_X124_X4only

```


#### Subsets

*inclN* = inclusion = what percent of all models have outcome (Y = 1) and this component (X = 1)
*covN* = necessity coverage = what percent of all models with this component (X = 1) have the outcome (Y = 1)
*RoN* = relevence of necessity = how trivial is a necessary condition trivial = 0 or relevant = 1
```{r qca}
sup_subset_X124 <- superSubset(dplyr::select(set_matrix_X124, -c(model, Xtest_Y, X1, X2, X4, outcome_full)), outcome = "outcome", ron.cut = 0.001)

sup_subset_full_X124 <- superSubset(dplyr::select(set_matrix_X124, -c(model, Xtest_Y, X1, X2, X4,)), outcome = "outcome_full", ron.cut = 0.001)

sup_subset_7_X124_nec <- superSubset(dplyr::select(set_matrix_7_X124, -c(model, outcome_full, Xtest_Y, X1, X2, X4)), outcome = "outcome", ron.cut = 0.001)

sup_subset_7_X124_suf <- superSubset(dplyr::select(set_matrix_7_X124, -c(model, outcome_full, Xtest_Y, X1, X2, X4)), outcome = "outcome", ron.cut = 0.001, relation = "sufficiency")

sup_subset_full_7_X124_X4only_nec <- superSubset(dplyr::select(set_matrix_7_X124_X4only, -c(model, outcome, Xtest_Y, X1, X2, X4)), outcome = "outcome_full", ron.cut = 0.001, relation = "necessity")

sup_subset_full_7_X124_X4only_suf <- superSubset(dplyr::select(set_matrix_7_X124_X4only, -c(model, outcome, Xtest_Y, X1, X2, X4)), outcome = "outcome_full", ron.cut = 0.001, relation = "sufficiency")

# sup_subset_X124
# #sup_subset_full_X124
# sup_subset_7_X124
sup_subset_7_X124_nec
sup_subset_7_X124_suf
sup_subset_full_7_X124_X4only_nec
sup_subset_full_7_X124_X4only_suf

```

## 2. Limited Path Certainty



```{r limp}

```


## Colophon

```{r cphon}
sessionInfo()
```

## References


```{r cite}
packages_cite %>%
  map(citation) %>%
  print(style = "text")
```
